---
title: 'Building a Better Graph'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if(!require("pacman")) install.packages("pacman")
pacman::p_load(
   here
  ,tidyverse
)
```


```{r}
tickets <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-03/tickets.csv")
```

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING")) %>% 
  count(violation_desc_condensed) %>%
  filter(str_detect(violation_desc_condensed, "LOAD"))
```


# Level 0: Base Plot

```{r}
theme_set(theme_gray())

tickets %>% 
  ggplot(aes(x = violation_desc)) +
  geom_bar()

ggsave(here::here("Level_00.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 1: Data Cleaning

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col()

ggsave(here::here("Level_01.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 2: Default Themes

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col() +
  theme_minimal()

ggsave(here::here("Level_02.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 3: scale_y_continuous + scales::comma

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal()

ggsave(here::here("Level_03.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 4: coord_flip + fct_reorder

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n)) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  coord_flip() +
  theme_minimal()

ggsave(here::here("Level_04.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 5: Window Dressing

* Change your axis labels with `labs`
* Change the color of your bar plot

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n)) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col(fill = "#E83536") +
  scale_y_continuous(labels = scales::comma) +
  coord_flip() +
  labs(x = "Violation Description",
       y = "Number of Tickets Issued",
       title = "Number of Tickets Issued by Violation Description") +
  theme_minimal()

ggsave(here::here("Level_05.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 6: Build Your Own Theme

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n)) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col(fill = "#E83536") +
  scale_y_continuous(labels = scales::comma) +
  coord_flip() +
  labs(x = "Violation Description",
       y = "Number of Tickets Issued",
       title = "Number of Tickets Issued by Violation Description") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto",
                            size = 10),
        axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "italic"),
        plot.title = element_text(face = "bold",
                                  size = 12))

ggsave(here::here("Level_06.png"),
       width = 8, height = 4.5, dpi = 300)
```

```{r}
# Build CompassRed theme
theme_compassred <- function () { 
  theme_minimal(base_size=10, base_family="Roboto") %+replace% 
    theme(axis.title = element_text(face = "bold"),
          axis.text = element_text(face = "italic"),
          plot.title = element_text(face = "bold",
                                    size = 12)
          
    )
}

theme_set(theme_compassred())
```

# Level 7: Layer Multiple Geometries

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n)) %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col(fill = "#E83536") +
  geom_label(aes(label = scales::comma(n)),
             size = 2.5,
             nudge_y = 30000) +
  scale_y_continuous(labels = scales::comma) +
  coord_flip() +
  labs(x = "Violation Description",
       y = "Number of Tickets Issued",
       title = "Number of Tickets Issued by Violation Description")

ggsave(here::here("Level_07.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 8: Highlight A Key Field

* Transform the data
* Move the fill to inside the aesthetic mapping
* Change colors with `scale_fill_manual`
* Remove the legend

```{r}
tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n),
         highlight = violation_desc_other == "Parking Prohibited") %>% 
  ggplot(aes(x = violation_desc_other,
             y = n)) +
  geom_col(aes(fill = highlight),
           alpha = 0.8) +
  geom_label(aes(label = scales::comma(n)),
             size = 2.5,
             nudge_y = 30000) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("gray75", "#E83536")) +
  coord_flip() +
  labs(x = "Violation Description",
       y = "Number of Tickets Issued",
       title = "Number of Tickets Issued by Violation Description") +
  guides(fill = "none")

ggsave(here::here("Level_08.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 9: Annotate

* Decide where to put the annotation and add a `geom_label`
* Build a 

```{r}
tickets_agg <- 
  tickets %>% 
  mutate(violation_desc_condensed = str_remove(violation_desc,
                                               " CC$"),
         violation_desc_condensed = str_trim(violation_desc_condensed),
         violation_desc_condensed = str_replace(violation_desc_condensed, "STOPPING", "STOP"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "HIWY", "HIGHWAY"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PROH\\w+", "PROHIBITED"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "(PARK) PROHIBITED", "PARKING"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "PASSENGR", "PASSENGER"),
         violation_desc_condensed = str_replace(violation_desc_condensed, "LOADNG", "LOADING"),
         violation_desc_other = fct_lump(f = violation_desc_condensed, n = 9),
         violation_desc_other = str_to_title(violation_desc_other)) %>% 
  count(violation_desc_other) %>% 
  mutate(violation_desc_other = fct_reorder(violation_desc_other, n),
         highlight = violation_desc_other == "Parking Prohibited")

ticket_note <- 
  paste("There appears to be different tiers of violations\n",
        "based upon the number of tickets issued.\n\n",
        "'Meter Expired' is in a tier of its own.\n\n",
        "'Parking Prohibited' ends the next tier.")

arrow_position <- data.frame(x_start = 4,
                             x_end   = 5,
                             y_start = 300000,
                             y_end   = 147000)

ggplot() +
  geom_col(data = tickets_agg,
           mapping = aes(x    = violation_desc_other,
                         y    = n,
                         fill = highlight),
           alpha = 0.8) +
  geom_label(data = tickets_agg,
             aes(x     = violation_desc_other,
                 y     = n,
                 label = scales::comma(n)),
             size = 2.5,
             nudge_y = 30000) +
  geom_label(data = filter(tickets_agg, 
                           highlight == T),
             mapping = aes(x     = violation_desc_other,
                           y     = n,
                           label = ticket_note),
             hjust = 0,
             nudge_x = -2.5,
             nudge_y = 80000,
             family = "Roboto",
             size = 3,
             fontface = "italic",
             label.r = unit(0, "lines")) +
  geom_curve(data = arrow_position,
             mapping = aes(x    = x_start,
                           y    = y_start,
                           xend = x_end,
                           yend = y_end),
             curvature = 0.1,
             size = 0.25,
             # color = "gray75",
             arrow = arrow(length = unit(0.015, "npc"),
                           type = "closed")) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("gray75", "#E83536")) +
  coord_flip() +
  labs(x = "Violation Description",
       y = "Number of Tickets Issued",
       title = "Number of Tickets Issued by Violation Description") +
  guides(fill = "none")

ggsave(here::here("Level_09.png"),
       width = 8, height = 4.5, dpi = 300)
```

# Level 10: Tidy it Up

```{r}
arrow_position <- data.frame(x_start = 3.85,
                             x_end   = 5,
                             y_start = 300000,
                             y_end   = 147000)

ggplot() +
  geom_col(data = tickets_agg,
           mapping = aes(x    = violation_desc_other,
                         y    = n,
                         fill = highlight),
           alpha = 0.8) +
  geom_label(data = tickets_agg,
             aes(x     = violation_desc_other,
                 y     = n,
                 label = scales::comma(n)),
             size = 2.5,
             nudge_y = 30000) +
  geom_label(data = filter(tickets_agg, 
                           highlight == T),
             mapping = aes(x     = violation_desc_other,
                           y     = n,
                           label = ticket_note),
             hjust = 0,
             nudge_x = -2.5,
             nudge_y = 80000,
             family = "Roboto",
             size = 3,
             fontface = "italic",
             label.r = unit(0, "lines")) +
  geom_curve(data = arrow_position,
             mapping = aes(x    = x_start,
                           y    = y_start,
                           xend = x_end,
                           yend = y_end),
             curvature = 0.1,
             size = 0.25,
             # color = "gray75",
             arrow = arrow(length = unit(0.015, "npc"),
                           type = "closed")) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("gray75", "#E83536")) +
  coord_flip() +
  labs(title = "Number of Tickets Issued by Violation Description") +
  guides(fill = "none") +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = -0.5))

ggsave(here::here("Level_10.png"),
       width = 8, height = 4.5, dpi = 300)
```

